Approximation as Differentiation

### 2025-05-24 main/introduction.tex
Tweaks questions in intro, placeholder for abstract.

Provenance tracking aims to answer questions like ``where did these data come from'', ``why are these data in the output'' and ``how were these data computed''. Program slicing is a collection of techniques for provenance tracking that attempts to take a run of a program and and areas of interest in the output and turn them into the subset of the input and the program that were responsible for generating those specific outputs.

>>>>

Provenance tracking aims to answer questions like ``Where did these data come from?'', ``Why are these data in the output?'' and ``How were these data computed?''. Program slicing is a collection of techniques for provenance tracking that attempts to take a run of a program and and areas of interest in the output and turn them into the subset of the input and the program that were responsible for generating those specific outputs.
